Analysis of Bauer et al. (unpublished) Field experiment: <br> Favourable Conservation Status (FCS)

### 2023-02-24 R/model_check_fcs.Rmd
Update model_check_fcs.Rmd

#### Prior predictive check (BARG 1.E)

```{r prior-predictive-check}
bayesplot::ppd_stat(yrep_prior[1:500, ], binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$site,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$exposition,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$survey_year_fct,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$target_type,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$seed_density,
                 binwidth = 0.1) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$sand_ratio,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$substrate_depth,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
```

>>>>

#### Prior predictive check - Kernel density (BARG 1.E)

```{r prior-predictive-check}
bayesplot::ppc_dens_overlay(yrep_prior[1:500, ])
ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$site) +
  coord_cartesian(xlim = c(-2, 2))
ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$exposition) +
  coord_cartesian(xlim = c(-2, 2))
ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$survey_year_fct) +
  coord_cartesian(xlim = c(-2, 2))
ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$target_type) +
  coord_cartesian(xlim = c(-2, 2))
ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$seed_density) +
  coord_cartesian(xlim = c(-2, 2))
ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$sand_ratio) +
  coord_cartesian(xlim = c(-2, 2))
ppc_dens_overlay_grouped(y, yrep_prior[1:500, ], group = sites$substrate_depth) +
  coord_cartesian(xlim = c(-2, 2))
```
